Efficient N-Dimensional surface estimation using Crofton formula and run-length encoding

### 2012-02-03 article/Article.tex
complete the intercept count algorithm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  hyperref should be the last package to be loaded.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dvips,
bookmarks,
bookmarksopen,
backref,
colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue},
]{hyperref}

@@

@@

@@

The perimeter estimation is now turned on by default, but can still disabled with \verb$SetComputePerimeter(false)$ in
\verb$itk::ShapeLabelMapFilter$ if not needed. This should enhance the user experience, especially for the attributes non obviously derived
from the perimeter like the roundness.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  hyperref should be the last package to be loaded.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dvips,
bookmarks,
bookmarksopen,
backref,
colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue},
]{hyperref}
% to be able to use options in graphics
\usepackage{graphicx}
% for pseudo code
\usepackage{listings}
% subfigures
\usepackage{subfigure}
\usepackage{pseudocode}

@@

The run-length encoding groups all the pixels on the same line in a single element. If the binary object is compact enough, as it is often the case for connected components, the run-length encoding heavily reduces the number of elements required to represent the object, compared to the simple pixel representation. Thanks to the run-length encoding, it is possible to compute the intercepts the binary object line by line, instead of computing it pixel by pixel.

The data structure used as the input of the algorigthm is a set of all the indexes of the object with their first element remove -- in 3D, this is all the possible (y, z) pairs -- to which are associated a list of lines. The lines are coded as a $x$ position and a length.

The algorithm used to count the intercepts is described in Figure \ref{interceptCountAlgo}.

\begin{figure}[htbp]
\centering
\small
\begin{pseudocode}[framebox]{countIntercept}{O}
\COMMENT{intercept count} \\
ic \GETS \emptyset \\
\COMMENT{the offset of the neighbors on the first axis} \\
xno \GETS offset(0) \\
xno[0] \GETS 1 \\
\FOREACH ls \in O \DO
\BEGIN
  \COMMENT{2 intercepts per line on the first axis} \\
  ic[xno] \GETS ic[xno] + 2 \cdot length(ls) \\
  \FOREACH nls \in neighbors(ls) \DO
  \BEGIN
    \COMMENT{straight and diagonal offsets of the neighbors} \\
    no \GETS offset(nls) \\
    dno \GETS offset(nls) \\
    dno[0] \GETS 1 \\
    \IF isEmpty(nls) \THEN
    \BEGIN
      \COMMENT{all the lines are on a contour} \\
      \FOREACH l \in ls \DO
      \BEGIN
	ic[no] \GETS ic[no] + length(l)\\
	ic[dno] \GETS ic[dno] + 2 \cdot length(l)
      \END
    \END
    \ELSE
    \BEGIN
      \COMMENT{iterate over the lines in $ls$ and the empty lines in $nls$} \\
      il \GETS iterator(ls) \\
      inl \GETS iterator(nls) \\
      nMin \GETS -\infty \\
      nMax \GETS pos(inl) - 1 \\
      \WHILE isNotAtEnd(il) \DO
      \BEGIN
        \COMMENT{measure the intersection of these two lines} \\
	ic[no] \GETS ic[no] + max( 0, min( lMax, nMax ) - max( lMin, nMin ) + 1 ) \\
	ic[dno] \GETS ic[dno] + max( 0, min( lMax, nMax+1 ) - max( lMin, nMin+1 ) + 1 )\\
	ic[dno] \GETS ic[dno] + max( 0, min( lMax, nMax-1 ) - max( lMin, nMin-1 ) + 1 )\\
        \COMMENT{and move to the next line, either in $ls$ or in $nls$} \\
	\IF nMax \leq lMax \THEN
	\BEGIN
          nMin \GETS pos(inl) + length(inl) \\
          next(inl) \\
          \IF isNotAtEnd(inl) \DO
            nMax \GETS pos(inl) - 1
          \ELSE
            nMax \GETS \infty
	\END
	\ELSE
          next(il)
      \END
    \END
  \END
\END
\end{pseudocode}
\caption{\label{interceptCountAlgo}The algorithm used to count the intercepts}
\end{figure}

@@

The perimeter estimation is now turned on by default, but can still be disabled with \verb$SetComputePerimeter(false)$ in
\verb$itk::ShapeLabelMapFilter$ if not needed. This should enhance the user experience, especially for the attributes non obviously derived
from the perimeter like the roundness.

@@
